\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{array}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{Document Number: YOUR-DOC-NUMBER}
\lhead{Your Document Title}
\rfoot{\thepage}

% Custom section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}
  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}

\begin{document}

\begin{titlepage}
\centering
{\LARGE \textbf{Algorithm Theoretical Baseline Document}}\\[1cm]
{\Large Your Project or Algorithm Name}\\[0.5cm]
Version: 1.0\\
Date: \today\\[2cm]

{\large Authors:}\\[0.5cm]
Your Name\\
Your Institute\\[2cm]

{\large Document Number: YOUR-DOC-NUMBER}\\[1cm]
\vfill
{\small © Copyright Year, Your Institution}
\end{titlepage}

\tableofcontents
\newpage

\section{Introduction}
\subsection{Observational Needs and Requirements}
\subsubsection{Direct Radiative Effect of Aerosols}
Your content here.

\subsubsection{Indirect Aerosol Radiative Forcing}
Your content here.

\subsubsection{Requirements}
Your content here. You can include tables:
\begin{table}[h!]
\centering
\begin{tabular}{lccc}
\toprule
Property & Glory & GCOS & ACE \\
\midrule
AOD & Value & Value & Value \\
SSA & Value & Value & Value \\
\bottomrule
\end{tabular}
\caption{Accuracy requirements on aerosol properties}
\end{table}

\subsection{Instrument Description}
Your instrument details here.

\subsection{Algorithm Overview}
Brief description of your algorithm.

\section{Algorithm Description}
\subsection{Full-Physics Retrieval}
\subsubsection{Forward Model}
Description and equations.

\subsubsection{Model Atmosphere and Optical Properties}
Description and equations.

\subsubsection{Surface Reflection Model}
Description and equations.

\subsubsection{Ocean Reflection Model}
Description and equations.

\subsection{Radiative Transfer Model}
Description and equations.

\subsection{Inversion Procedure}
Detailed explanation.

\section{Performance Analysis}
Your analysis here.

\section{Feasibility}
Discussion on algorithm feasibility.

\appendix
\section{Additional Details}
Additional technical details.

\newpage
\section*{Document Change Record}
\begin{tabular}{lp{2cm}p{8cm}}
\toprule
Issue & Date & Comments \\
\midrule
1.0 & YYYY-MM-DD & Initial Release \\
\bottomrule
\end{tabular}

\newpage
\section*{References}
\begin{thebibliography}{99}
\bibitem{key} Author(s). \textit{Title}. Journal/Publisher, Year.
\end{thebibliography}

\end{document}
